template for CV in RCC

### 2018-01-06 analysis/CVtemplate.Rmd
Files commited by wflow_commit.

---
title: "template for CV in RCC"
author: "Wei"
date: 10-03
output: html_document
---

@@

```{r}
library(R.matlab)
# call the R functions
source("~/HG/flash/data/CVmissflashr2/template/Rfunction.R")
# read the data
# you need to change the path for different data
Y_data = R.matlab::readMat("~/HG/flash/data/CVmissflashr2/Breastcancer/example.mat")
Y = Y_data$Y
N = dim(Y)[1]
P = dim(Y)[2]
Y = Y - rowMeans(Y) %*% t(rep(1,P))
result = c()
missindex = miss_gen(Y, percent = 0.1)
# creat a folder for the output and matlab in the folder we make
if(file.exists("NBSFAout")){
  unlink("NBSFAout", recursive= T)
}
system("mkdir NBSFAout")
# write the missing index
writeMat("./NBSFAout/missindex.mat", missindex = missindex)

>>>>

---
title: "template for CV in RCC"
author: "Wei"
date: 10-03
output: 
  html_document:
    code_folding: hide
---

@@

```
library(R.matlab)
# call the R functions
source("~/HG/flash/data/CVmissflashr2/template/Rfunction.R")
# read the data
# you need to change the path for different data
Y_data = R.matlab::readMat("~/HG/flash/data/CVmissflashr2/Breastcancer/example.mat")
Y = Y_data$Y
N = dim(Y)[1]
P = dim(Y)[2]
Y = Y - rowMeans(Y) %*% t(rep(1,P))
result = c()
missindex = miss_gen(Y, percent = 0.1)
# creat a folder for the output and matlab in the folder we make
if(file.exists("NBSFAout")){
  unlink("NBSFAout", recursive= T)
}
system("mkdir NBSFAout")
# write the missing index
writeMat("./NBSFAout/missindex.mat", missindex = missindex)
